Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-04 paper/ms.tex
update paper

\begin{figure}[!t]
	\gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    (IN PROGRESS) Significance thresholds empirically defined for the
    transiting planet search described in
    \S~\ref{subsec:identifying_ctois}.  Each point represents the TLS
    periodogram peak signal detection efficiency from one light curve.
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

>>>>

\begin{figure}[!t]
	\gridline{\fig{tls_sde_vs_period_scatter.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\bf Transiting planet search periodogram summary.}
    Each point represents the TLS periodogram peak signal detection
    efficiency (SDE) and corresponding period from one light curve.
    Significance thresholds (orange lines) are empirically defined for
    the transiting planet search described in
    \S~\ref{subsec:identifying_ctois}.  
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}
